IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2015-01-15 paper/real.tex
r2; address wrapping question

While the described system implements |specLangJS seqf|, applications
typically require access to libraries (e.g., the file system library
\textsf{fs}) that have external effects.
%
Exposing the Node.js APIs directly to sandboxed tasks is unsafe.
Instead, we implement libraries (like a labeled version of \textsf{fs}) as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Fig.~\ref{fig:node}) and the main Node.js task that implements
the IFC monitor.
%
While this is safer than simply wrapping unsafe objects, which can
potentially be exploited to access objects outside the context, adding
features such as the \textsf{fs} requires the code in the main task to
ensures that labels are properly propagated and enforced.
%
Unfortunately, while imposing such a proof burden
is undesirable, this also has to be expected:
different language environments expose different libraries for
handling external I/O, and the correct treatment of external effects
is application specific.
%
%% For instance, in the case of Node.js, how labels interact with the
%% file system may even vary according to the application (e.g.,
%% in the IFC system Hails~\cite{hails}, labels are not persisted).
%
%While we can extend our formalism to model a particular interface to
%the file system, HTTP client, etc. the utility of this formalization is
%unclear and left to future work.
%
We do not extend our formalism to account for the  particular
interface to the file system, HTTP client, etc., as this is
specific to the Node.js implementation and does not generalize
to other systems.

>>>>

While the described system implements |specLangJS seqf|, applications
typically require access to libraries (e.g., the file system library
\textsf{fs}) that have external effects.
%
Exposing the Node.js APIs directly to sandboxed tasks is unsafe.
Instead, we implement libraries (like a labeled version of \textsf{fs}) as
message exchanges between the sandboxed tasks (e.g., \textsf{task-1}
in Fig.~\ref{fig:node}) and the main Node.js task that implements
the IFC monitor.
%
While this is safer than simply wrapping unsafe objects, which can
potentially be exploited to access objects outside the context (e.g.,
as seen with ADSafe, FBJS, and Caja~\cite{taly2011automated,
maffeis2010object, maffeis2009language}), adding features such as the
\textsf{fs} requires the code in the main task to ensures that labels
are properly propagated and enforced.
%
Unfortunately, while imposing such a proof burden
is undesirable, this also has to be expected:
different language environments expose different libraries for
handling external I/O, and the correct treatment of external effects
is application specific.
%
%% For instance, in the case of Node.js, how labels interact with the
%% file system may even vary according to the application (e.g.,
%% in the IFC system Hails~\cite{hails}, labels are not persisted).
%
%While we can extend our formalism to model a particular interface to
%the file system, HTTP client, etc. the utility of this formalization is
%unclear and left to future work.
%
We do not extend our formalism to account for the  particular
interface to the file system, HTTP client, etc., as this is
specific to the Node.js implementation and does not generalize
to other systems.
